### 2010-02-23 trunk/deliverables/D2_2_Ontology/properties.tex
review-ready version ready
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@589 d8b0c59b-6544-0410-94d9-83a5658a058e

\textcolor{white}{\textbf{domain}} & \htmlref{\texttt{fgo:Definition}}{subs:Definition}, \htmlref{\texttt{fgo:Resource}}{subs:Resource} \\ \hline
\textcolor{white}{\textbf{range}} & \htmlref{\texttt{fgo:ResourceReference}}{subs:ResourceReference} \\ \hline

@@

\textcolor{white}{\textbf{description}} & This property indicates which actions are asociated and can be perfomed within 

@@

\textcolor{white}{\textbf{description}} & URL of the executable code of a particular screen. \\ \hline

@@

@@

\subsubsection*{Property: \texttt{fgo:hasCondition}}
\label{subs:hasCondition}

@@

\textcolor{white}{\textbf{label}} & has condition \\ \hline
\textcolor{white}{\textbf{description}} & This property links a precondition or postcondition to a certain condition. \\ \hline

@@

\textcolor{white}{\textbf{domain}} & \htmlref{\texttt{fgo:Postcondition}}{subs:Postcondition}, \htmlref{\texttt{fgo:Precondition}}{subs:Precondition} \\ \hline
\textcolor{white}{\textbf{range}} & \htmlref{\texttt{fgo:Condition}}{subs:Condition}, \texttt{rdf:Bag} \\ \hline
\subsubsection*{Property: \texttt{fgo:hasDefinition}}
\label{subs:hasDefinition}
\textcolor{white}{\textbf{label}} & has definition \\ \hline
\textcolor{white}{\textbf{description}} & The structure and behaviour of a resource. \\ \hline
\textcolor{white}{\textbf{domain}} & \htmlref{\texttt{fgo:Resource}}{subs:Resource} \\ \hline
\textcolor{white}{\textbf{range}} & \htmlref{\texttt{fgo:Definition}}{subs:Definition} \\ \hline

@@

\textcolor{white}{\textbf{domain}} & \htmlref{\texttt{fgo:Resource}}{subs:Resource} \\ \hline

@@

\subsubsection*{Property: \texttt{fgo:hasId}}
\label{subs:hasId}
\textcolor{white}{\textbf{label}} & has id \\ \hline
\textcolor{white}{\textbf{description}} & The internal ID of the resource within the container resource. \\ \hline
\textcolor{white}{\textbf{domain}} & \htmlref{\texttt{fgo:Resource}}{subs:Resource}, \htmlref{\texttt{fgo:ResourceReference}}{subs:ResourceReference} \\ \hline

@@

@@

\subsubsection*{Property: \texttt{fgo:hasName}}
\label{subs:hasName}
\textcolor{white}{\textbf{label}} & has name \\ \hline
\textcolor{white}{\textbf{description}} & The name the user gives to the resource. \\ \hline
\textcolor{white}{\textbf{domain}} & \htmlref{\texttt{fgo:Resource}}{subs:Resource} \\ \hline

@@

@@

\textcolor{white}{\textbf{description}} & This property links a screen or screenflow to its pre-condition, 
    i.e., the facts that need to be fulfilled in order for this screen or screenflow 
    to be reachable. \\ \hline

@@

\textcolor{white}{\textbf{description}} & This property is the textual representation of a condition. \\ \hline

@@

\textcolor{white}{\textbf{range}} & \htmlref{\texttt{fgo:Condition}}{subs:Condition}, \texttt{rdf:Bag} \\ \hline

@@

\textcolor{white}{\textbf{range}} & \htmlref{\texttt{fgo:Condition}}{subs:Condition}, \texttt{rdf:Bag} \\ \hline

@@

\subsubsection*{Property: \texttt{fgo:hasSource}}
\label{subs:hasSource}
\textcolor{white}{\textbf{label}} & has source \\ \hline
\textcolor{white}{\textbf{description}} & URL of the source code of a particular library. \\ \hline
\subsubsection*{Property: \texttt{fgo:hasTag}}
\label{subs:hasTag}
\textcolor{white}{\textbf{label}} & has tag \\ \hline
\textcolor{white}{\textbf{description}} & A tag is used to annotate keywords of a particular resource. \\ \hline
\textcolor{white}{\textbf{domain}} & \htmlref{\texttt{fgo:Resource}}{subs:Resource} \\ \hline

@@

\textcolor{white}{\textbf{description}} & This property represents the events fired within a building block. e.g. a 
	button to clear the shopping cart will fired a "clear cart" trigger. \\ \hline

@@

\subsubsection*{Property: \texttt{fgo:hasType}}
\label{subs:hasType}
\textcolor{white}{\textbf{label}} & has type \\ \hline
\textcolor{white}{\textbf{description}} & The type of the resource. \\ \hline
\textcolor{white}{\textbf{domain}} & \htmlref{\texttt{fgo:Resource}}{subs:Resource} \\ \hline
\subsubsection*{Property: \texttt{fgo:hasUri}}
\label{subs:hasUri}
\textcolor{white}{\textbf{label}} & has uri \\ \hline
\textcolor{white}{\textbf{description}} & URI of a particular resource pointing from a reference within
	another resource. \\ \hline
\textcolor{white}{\textbf{domain}} & \htmlref{\texttt{fgo:ResourceReference}}{subs:ResourceReference} \\ \hline

@@

\textcolor{white}{\textbf{range}} & \htmlref{\texttt{fgo:ResourceReference}}{subs:ResourceReference} \\ \hline
\subsubsection*{Property: \texttt{fgo:hasVersion}}
\label{subs:hasVersion}
\textcolor{white}{\textbf{label}} & has version \\ \hline
\textcolor{white}{\textbf{description}} & The version of a particular screen or screenflow, such as 1.0, 0.2beta, etc. \\ \hline
\textcolor{white}{\textbf{domain}} & \htmlref{\texttt{fgo:Resource}}{subs:Resource} \\ \hline
\subsubsection*{Property: \texttt{fgo:integratesTerm}}
\label{subs:integratesTerm}
\textcolor{white}{\textbf{label}} & integratesTerm \\ \hline
\textcolor{white}{\textbf{description}} & A way to explicitly say that an ontology uses terms from another namespace. 
    Maybe a bit redundant, but why not. TODO: Must be moved to a different namespace! \\ \hline

@@

	or both of them. This will define when they have to be taken into account by the

>>>>

\textcolor{white}{\textbf{domain}} & \htmlref{\texttt{fgo:BuildingBlock}}{subs:BuildingBlock} \\ \hline
\textcolor{white}{\textbf{range}} & \htmlref{\texttt{fgo:BuildingBlock}}{subs:BuildingBlock} \\ \hline

@@

\textcolor{white}{\textbf{description}} & This property indicates which actions are associated and can be perfomed within 

@@

\textcolor{white}{\textbf{description}} & URL of the executable code of a particular building block (currently screens or screen components). \\ \hline
\textcolor{white}{\textbf{domain}} & \htmlref{\texttt{fgo:WithCode}}{subs:WithCode} \\ \hline
\subsubsection*{Property: \texttt{fgo:hasForm}}
\label{subs:hasForm}
\textcolor{white}{\textbf{label}} & has form \\ \hline
\textcolor{white}{\textbf{description}} & If a screen is defined declaratively, this property links it to its form (i.e., its visual user interface). \\ \hline

@@

\textcolor{white}{\textbf{range}} & \htmlref{\texttt{fgo:Form}}{subs:Form} \\ \hline

@@

\subsubsection*{Property: \texttt{fgo:hasFormElement}}
\label{subs:hasFormElement}

@@

\textcolor{white}{\textbf{label}} & has form element \\ \hline
\textcolor{white}{\textbf{description}} & If a form is defined declaratively, its elements are linked to it with this property. \\ \hline

@@

\textcolor{white}{\textbf{domain}} & \htmlref{\texttt{fgo:Form}}{subs:Form} \\ \hline
\textcolor{white}{\textbf{range}} & \htmlref{\texttt{fgo:FormElement}}{subs:FormElement} \\ \hline

@@

\textcolor{white}{\textbf{domain}} & \htmlref{\texttt{fgo:BuildingBlock}}{subs:BuildingBlock} \\ \hline

@@

@@

\textcolor{white}{\textbf{domain}} & \htmlref{\texttt{fgo:WithCode}}{subs:WithCode} \\ \hline

@@

@@

\subsubsection*{Property: \texttt{fgo:hasOperator}}
\label{subs:hasOperator}
\textcolor{white}{\textbf{label}} & has operator \\ \hline
\textcolor{white}{\textbf{description}} & If a screen is defined declaratively, this property links it to an operator it might contain. \\ \hline
\textcolor{white}{\textbf{range}} & \htmlref{\texttt{fgo:Operator}}{subs:Operator} \\ \hline

@@

\textcolor{white}{\textbf{description}} & This property links the abstract representation of a fact (i.e., an RDF triple) in FAST to a graph resource containing the actual triple. \\ \hline

@@

\textcolor{white}{\textbf{description}} & This property links to the textual representation of a fact (i.e., an RDF triple), e.g., in N3. \\ \hline

@@

\textcolor{white}{\textbf{range}} & \htmlref{\texttt{fgo:Condition}}{subs:Condition} \\ \hline

@@

\textcolor{white}{\textbf{range}} & \htmlref{\texttt{fgo:Condition}}{subs:Condition} \\ \hline
\subsubsection*{Property: \texttt{fgo:hasResource}}
\label{subs:hasResource}
\textcolor{white}{\textbf{label}} & has resource \\ \hline
\textcolor{white}{\textbf{description}} & If a screen is defined declaratively, this property links it to its service resource (i.e., its backend). \\ \hline
\textcolor{white}{\textbf{range}} & \htmlref{\texttt{fgo:Resource}}{subs:Resource} \\ \hline

@@

@@

\textcolor{white}{\textbf{description}} & This property links a buildiong block to a Trigger. \\ \hline

@@

\textcolor{white}{\textbf{range}} & \htmlref{\texttt{fgo:Trigger}}{subs:Trigger} \\ \hline

@@

@@

or both of them. This property will define when they have to be taken into account by the
